Full Title

### 2019-10-14 draft/paper.tex
some symbolic execution

Text of paper \ldots

@@

\cite{Siddiqui:2012:SSE:2245276.2231988}

>>>>

"building a symbolic compiler is often the most difficult aspect of
creating solver-aided tools, especially for general-purpose languages" \cite{Torlak:2014:LSV:2594291.2594340}

@@

Our technique should not be confused with
\citet{Siddiqui:2012:SSE:2245276.2231988}'s staged symbolic execution, which
performs symbolic execution in stages. Different from a compilation-based
staging in this paper, their first stage generates abstract symbolic inputs,
which then will be shared and used across other methods in the second stage.
